data cleaning logs

### 2021-06-23 conditions.Rmd
Update on Cleaning and Conditions
A function for removing notes and updated condition logs

```{r}
##Flag if HH reports that a child dropped out of school as a coping strategy for a lack of food, but also reports either (1) having no children in the house or (2) having no children dropped out of school
df <- df %>% 
  mutate(childdropout_check = case_when( children_dropout == "yes" & (tot_children == 0 | dropout == 0) ~ "Flagged", TRUE~ ""))

@@

df <- df %>% 
  mutate(childlabour_check = case_when( child_labour == "yes" & (tot_children == 0 | under_18_working == "no" ) ~ "Flagged", TRUE~ ""))

@@

```{r}
##Flag if reported shelter is tent, but HH reports having defects related to windows, floors, or foundation
df <- df %>%
      mutate(tent_check = case_when(df$shelter_type_inperson == "tent" & (shelter_issues !="none")~ "Flagged", TRUE ~ "" ))
```
```{r}
df12 <- df %>% 
      #filter(tent_check == "Flagged") %>% 
       dplyr::select(tent_check, shelter_type_inperson, shelter_issues)
head(df12)
```

@@

df <- df %>% 
    mutate(gender_check = case_when(df$gender_respondent_r == df$gender_respondent_r2 ~ "Flagged", TRUE ~ ""))
```

@@

```{r}
df23<- df %>% 
        #filter(distance_check == "Flagged") %>% 
        dplyr::select(distance_check,distance_hospital)
head(df23)
```
```{r}
 ##if remote_learning == dropout
df <- df %>% 
      mutate(remote_learning_check = case_when(remote_learning == dropout ~ "Flagged", TRUE ~ ""))
```
```{r}
df24<- df %>% 
        filter(remote_learning_check == "Flagged") %>% 
        dplyr::select(remote_learning_check,remote_learning, dropout)
df24
```
```{r}
##if tot_income == 0

>>>>

```{r}
##Flag if HH reports that a child dropped out of school as a coping strategy for a lack of food, but also reports either (1) having no children in the house or (2) having no children dropped out of school
df <- df %>% 
  mutate(childdropout_check = case_when( coping_children_dropout == "yes" & (tot_children == 0 | dropout_num == 0) ~ "Flagged", TRUE~ ""))

@@

df <- df %>% 
  mutate(childlabour_check = case_when( coping_child_labour == "yes" & (tot_children == 0 | under_18_working == "no" ) ~ "Flagged", TRUE~ ""))

@@

```{r}
##Flag if reported shelter is tent, but HH reports having defects related to windows, floors, or foundation
df <- df %>%
      mutate(tent_check = case_when(df$shelter_type == "tent" & (shelter_issues !="none")~ "Flagged", TRUE ~ "" ))
```
```{r}
df12 <- df %>% 
      #filter(tent_check == "Flagged") %>% 
       dplyr::select(tent_check, shelter_type_inperson, shelter_issues)
head(df12)
```

@@

df <- df %>% 
    mutate(gender_check = case_when(df$gender_respondent == df$gender_respondent ~ "Flagged", TRUE ~ ""))
```

@@

```{r}
df23<- df %>% 
        #filter(distance_check == "Flagged") %>% 
        dplyr::select(distance_check,distance_hospital)
head(df23)
```
```{r}
 ##if remote_learning == dropout
df <- df %>% 
      mutate(remote_learning_check = case_when(remote_learning == dropout_num ~ "Flagged", TRUE ~ ""))
```
```{r}
df24<- df %>% 
        filter(remote_learning_check == "Flagged") %>% 
        dplyr::select(remote_learning_check,remote_learning, dropout)
df24
```
```{r}
##if tot_income == 0
